QPLIB: A Library of Quadratic Programming Instances

### 2018-08-28 AnswerToTheReferees2_second.tex

\newcommand{\leo}[1]{{\color{red}#1}}
\newcommand{\fabio}[1]{{\color{cyan}#1}}
\newcommand{\emiliano}[1]{{\color{blue}#1}}   
\newcommand{\antonio}[1]{{\color{ForestGreen}#1}}     
\newcommand{\andrea}[1]{{\color{blue}{\bf #1}}}

\begin{document}

\section*{QPLIB: a Library of a Quadratic Programming Instances (MPC-022017-00003)-- Comments of the minor revision}

\rep{
 Following the Associate and Area Editor suggestions, we 
 performed a minor revision of our manuscript. We carefully took into account all the comments made by the AE.
 The new submitted document highlights in green the text that has been
added or changed.
In the following, the comments of the AE, together with our point-by-point replies.
}

@@

\rep{We would like to thank the AE for his/her positive opinion on the revision we performed of our manuscript. 
%\leo{Togliamo la spiegazione degli algoritmi e sostituiamola con una citazione di un book-tutorial-survey-introduction.}
}

\bigskip
\textbf{Main points:}

\begin{itemize}
\item 
{\it
[from referee, paraphrased] 8. Please try to find a more precise definition of asypmtotically complete algorithm to 
cite.
}

\rep{We have added the definition of asypmtotically complete algorithms to Section 2.3.3. The definition has been taken from: 
\begin{itemize}
\item Neumaier, A.: Complete search in continuous global optimization and
constraint satisfaction. Acta Numerica 13, 271–369 (2004)
\end{itemize}
}
